---
title: "Democratizing Modern Art"
subtitle: "Customizable Artworks using Shiny App"
author: "Viz Biz <br> Eli, Lilly, Phillip, Sana"
institute: "Duke University"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}
library(tidyverse)
library(knitr)
library(viridis)
library(xaringanthemer)
library(ggrepel)
library(scales)
library(gganimate)
library(gridExtra)
```

```{r setup, include = FALSE}
# For better figure resolution
knitr::opts_chunk$set(
  fig.retina = 3, 
  dpi = 300, 
  fig.width = 6, 
  fig.asp = 0.618, 
  out.width = "70%"
  )
```

```{r load-data, include = FALSE}
```

```{r style-slides, echo = FALSE}
style_xaringan(
  title_slide_background_image = "img/watercolour_sys02_img32_percolate.jpg"
)
```

Class: middle, inverse, center

### Big Picture

**Goal:** Make expensive, luxury modern artworks that are once accessible only in museum and private
collections to be accessible to the public mass.

- We will make our chosen artworks *customizable* and reproducible using the Shiny App.

- Users will be able to download their own customized artwork with their desired resolution or 
quality level.

**Project Main Question**: Can we recreate famous artworks and make them customizable through computer programming? 

---

### Our Chosen Artworks

- Frank Stella, *Lettre sur les sourds et muets II* (1974)

- Piet Mondrian, *Trafalgar Square* (1939-1943)

- Wassily Kandinsky, *Composition 8* (1923)

- Barbara Kruger, *Untitled (Your body is a battleground)* (1989)

---

### Demo

We will demo you to our final Shiny App with a click [***here***](https://phillipharmadi.shinyapps.io/final-shiny/).

Please raise your hand at **anytime** if you want to be shown specific reactive features during our demonstration.
